\documentclass[11pt]{article}

% --- Packages ---
\usepackage[usenames, dvipsnames]{color} % Cool colors
\usepackage{enumerate, amsmath, amsthm, amssymb, mathrsfs, algorithm, algpseudocode, fontawesome, pifont, subfig, fullpage, csquotes, dashrule, tikz, bbm, booktabs, bm, hyperref, wasysym}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage[numbers]{natbib}
\usepackage[normalem]{ulem}

% --- Misc. ---
\hbadness=10000 % No "underfull hbox" messages.
\setlength{\parindent}{0pt} % Removes all indentation.

% -- Commands --
\input{commands}

% Nice coloring of references.
\usepackage{hyperref}
\hypersetup{               
    colorlinks=true,              
    breaklinks=true,               
    urlcolor=dblue,
    linkcolor=dgreen,
    linkbordercolor=dgreen,
    citecolor=dblue,
    citebordercolor=dblue
}



\title{RLDM 2019 Notes \\ \Large{Montreal, Canada}}
\author{David Abel\footnote{\durl{http://david-abel.github.io}} \\ \durl{david_abel@brown.edu}}
\date{July 2019}

\begin{document}
\maketitle
\tableofcontents
\newpage


This document contains notes I took during the events I managed to make it to at RLDM 2019 in Montreal, Canada. Please feel free to distribute it and shoot me an email at \durl{david_abel@brown.edu} if you find any typos or other items that need correcting. 


\section{Conference Highlights}

I {\it adore} RLDM. It's a great size, the talks are a mixture of diverse, thought provoking, and fun, and I always come up away with a lengthy paper list, new connections, and tons to think about. Very excited for RLDM 2021 (at Brown, too)!. \\

A few things to mention:
\begin{enumerate}
    \item {\it Hot topics:} Some nice work rethinking {\it time} in RL in some manner or another: rethinking the discount (work by~\citet{fedus2019hyperbolic}) or rethinking temporal abstraction (work by~\citet{harutyunyan2019termination}). Also, several great talks suggesting we should rethink our objectives: Sheila McIlraith's talk (Section~\ref{sec:rm}) and Tom Griffiths talk (Section~\ref{sec:tg}.
    
    \item Both of Will Dabney's talks were amazing! See Section~\ref{sec:will-neuro} and Section~\ref{sec:will-a}.
    
    \item The ever-curious interplay of model-based and model-free came up in discussion quite a lot. I particularly enjoyed Fiery Cushman's talk in this space! (see Section~\ref{sec:fc}).
    
    \item Really excited to see what happens in the MineRL competition---more details in Katja Hofmann's talk (Section~\ref{sec:kh}).
    
    \item Rich Sutton closed out the conference with a talk titled {\it play} that was packed with lots of nice insights.
    
    \item Emma Brunskill's tutorial on batch RL was fantastic (Lots of pointers to great recent literature I plan to read).
\end{enumerate}


% ------------
% -- Sunday --
% ------------
\newpage
\section{Sunday July 7th: Tutorials}
\input{days/sunday_7_7_19.tex}



% ------------
% -- Monday --
% ------------
\newpage
\section{Monday July 8th: Main Conference}
\input{days/monday_7_8_19.tex}



% ------------
% -- Tuesday --
% ------------
\newpage
\section{Tuesday July 9th: Main Conference}
\input{days/tuesday_7_9_19.tex}


% --------------
% -- Wednesday --
% --------------
\newpage
\section{Wednesday July 10th: Main Conference and Workshops}
\input{days/wednesday_7_10_19.tex}




% --- Bibliography ---
\newpage
\bibliographystyle{plainnat}
\bibliography{rldm}

\end{document}